### 2019-12-19 README.Rmd
fix documentation errors
updates README to include vis_binary

- `vis_guess()` visualise the individual class of earch value in your data

@@

>>>>

- `vis_guess()` visualise the individual class of each value in your data
- `vis_value()` visualise the value class of each cell in your data
- `vis_binary()` visualise the occurrence of binary values in your data

@@

## Using `vis_binary()`

`vis_binary()` visualises binary values. See below for use with example data, `dat_bin`

```{r vis-bin}
vis_binary(dat_bin)
```

If you don't have only binary values a warning will be shown.

```{r vis-bin-airq, eval = FALSE}
vis_binary(airquality)
```

```
Error in test_if_all_binary(data) : 
  data input can only contain binary values - this means either 0 or 1, or NA. Please subset the data to be binary values, or see ?vis_value.
```
